---
title: "An strange article about a template with a very bad title"
author:
- name: Jane Doe
  affiliation: Some University
abstract: "This document serves as a template that you can reuse with your own projects.  The goal is to illustrate some of the functionalities of R, LaTeX, and Rmarkdown to conduct end-to-end academic research projects. You will also use this template for some of the course assignments and also to do your research project. There are many different moving pieces when you use this document for the first time. Don't worry if you don't understand everything yet."
keywords: "GitHub, LaTex, R, Rmarkdown, RStudio"
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: references.bib
biblio-style: apsr

geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
endnote: no
output:
  pdf_document:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    latex_engine: pdflatex
    template: latex-template.tex
header-includes:
  -  \usepackage{hyperref}
# spacing: double
---

```{r setup, include=FALSE}
# Setup and Compiling Options
set.seed(42)
source("requirements.R")
knitr::opts_chunk$set(fig.path='figs/',
                      message=FALSE, warning=FALSE, cache=FALSE,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })
```


# Introduction

Theories of political disagreement often envisage ideology as a single, latent dimension that structures politics on a continuum between left and right [@downs1957economic]. `r lorem::ipsum(2, avg_words_per_sentence = 15)`

## How do we make citations and automate reference lists in RMarkdown documents ?

```{markdown}
- Add your reference(s) to a `refernces.bib` file.
- Find the bib key in your `refernces.bib` file.
- Put an @ before the bib key (e.g. @downs1957economic)
- @downs1957economic creates an in-text citation (e.g. Downs (1957) says...)
- [@downs1957economic] creates a parenthetical citation (Downs, 1957)
```

`r lorem::ipsum(2, avg_words_per_sentence = 15)`


## Existing work

Not only you can have figures but you can also add footnotes [^one_footnote] in Rmarkdown. Here's another one.[^another_footnote] `r lorem::ipsum(1, avg_words_per_sentence = 20)`

```{r, eval=TRUE, echo=FALSE, size="small", fig.cap="A Figure That Needs a Better Title", out.width="75%", fig.align="center"}
library(tidyverse)
library(anesr)
data(timeseries_2016)

timeseries_2016 %>%
  filter(between(V162034a, 1, 4)) %>%
  ggplot(aes(x=as.numeric(V162034a), y = ..prop..*100, fill=as.factor(..x..))) +
  geom_bar(alpha=.5) +
  geom_text(
    aes(label=scales::percent(..prop..), y=..prop..*100), stat="count", vjust = -.5
  ) +
  ylab("Percentage (%)") +
  xlab("Candidates") +
  theme_minimal() +
  theme(legend.position="none") +
  scale_x_discrete(
    limits=c("1"="H. Clinton", "2"="D. Trump", "3"="G. Johnson", "4"="J. Stein")
  ) +
  scale_fill_brewer(limits=c("2", "1", "4", "3"), palette="Set1")

```

`r lorem::ipsum(1, avg_words_per_sentence = 20)`

[^one_footnote]: I really hope that you noticed this footnote.
[^another_footnote]: Some extra random text, just to make sure you see these little footnotes.


## Research question

The filler text above and below should somehow lead to a research question and illustrate why it matters. The question needs to be clearly stated. At the end of this section you emphasize you hypotheses. `r lorem::ipsum(1, avg_words_per_sentence = 16)`

$H_1$: Given what we know, we expect something to happen.

$H_2$: We might expect another thing to happen.

$H_3$: ...

# Data and Methods

By the way, did you notice that we are using real data from the American National Election  Study[^anes]. `r lorem::ipsum(1, avg_words_per_sentence = 19)`

[^anes]: https://electionstudies.org/data-center/2016-time-series-study/

```{r, eval=TRUE, echo=FALSE, size="small", fig.cap="Another Figure That Needs a Better Title", out.width="75%", fig.align="center"}

tmp_df <- timeseries_2016 %>%
  select(V161126, V161181, V161184, V161178) %>%
  filter(
    between(V161126, 1, 7),
    between(V161181, 1, 7),
    between(V161184, 1, 7),
    between(V161178, 1, 7)
  ) %>%
  rename(
    "Ideology"="V161126",
    "Defense"="V161181",
    "Healthcare"="V161184",
    "Government"="V161178"
  ) %>%
  gather(key, value)

ggplot(tmp_df, aes(x=value, y=..prop.., group=key)) +
  geom_bar(alpha=.5) +
  facet_wrap(~key) +
  ylab("Percentage (%)") +
  xlab("These labels need to be fixed...") +
  theme_minimal() +
  theme(legend.position="none")

```

Here are some variables that we could use to build interesting features. `r lorem::ipsum(1)`

```{r, eval=TRUE, echo=FALSE, size="small", fig.cap="Maybe Add a Title Here That Makes More Sense?", out.width="75%", fig.align="center"}

tmp_df <- timeseries_2016 %>%
  select(V161031, V161086, V161087) %>%
  rename(
    "vote_intent"="V161031",
    "ft_democrat"="V161086",
    "ft_republican"="V161087"
  ) %>%
  filter(
    between(vote_intent, 1,4),
    ft_democrat>=0,
    ft_republican>=0
  )

tmp_df %>%
  ggplot(
    aes(x=as.numeric(ft_republican), y=as.numeric(ft_democrat), color=as.factor(vote_intent))
  ) +
  geom_jitter(shape=1, width=5, height=5, alpha=.66) +
  geom_smooth(se=FALSE, size=2, color="grey", alpha=.8) +
  ylab("Democrat Feeling Thermometer") +
  xlab("Republican Feeling Thermometer") +
  ylim(c(0,100)) +
  xlim(c(0,100)) +
  scale_color_brewer(
    limits=c("2", "1", "4", "3"),
    palette="Set1",
    labels=c("D. Trump", "H. Clinton", "J. Stein", "G. Johnson"),
    name='Change Me'
  ) +
  theme_minimal()

```

`r lorem::ipsum(2, avg_words_per_sentence = 20)`

# Results

Well, here are some fitted models. Are these any good?
`r lorem::ipsum(3, avg_words_per_sentence = 15)`

```{r, echo=FALSE, eval=TRUE, tidy = TRUE, size="small", results="asis", out.width="75%", fig.align="center"}

library(stargazer)

tmp_df <- timeseries_2016 %>%
  select(
    V161031,  # vote_intent
    V161086,  # ft_democrat
    V161087,  # ft_republican
    V161126,  # ideology
    V161181,  # defense
    V161184,  # healthcare
    V161178,  # government
    V161155   # party_id
  ) %>%
  rename(
    "vote_intent"="V161031",
    "ft_democrat"="V161086",
    "ft_republican"="V161087",
    "ideology"="V161126",
    "defense"="V161181",
    "healthcare"="V161184",
    "government"="V161178",
    "party_id"="V161155"
  ) %>%
  filter(
    between(vote_intent, 1,2),
    ft_democrat>=0,
    ft_republican>=0,
    between(ideology, 1,7),
    between(defense, 1,7),
    between(healthcare, 1,7),
    between(government, 1,7),
    between(party_id, 1,3)
  ) %>%
  mutate(
    trump_int = if_else(vote_intent==2, 1, 0),
    ft_diff = as.numeric(ft_republican-ft_democrat),
    party_id = as.factor(party_id),
    ideology = as.numeric(ideology),
    defense = as.numeric(defense),
    healthcare = as.numeric(healthcare),
    government = as.numeric(government),
  )

model_1 <- trump_int ~ ft_diff + party_id
model_2 <- trump_int ~ ft_diff + party_id + ideology
model_3 <- trump_int ~ ft_diff + party_id + ideology + defense + healthcare + government

fit_1 <- glm(model_1, data=tmp_df,family=binomial())
fit_2 <- glm(model_2, data=tmp_df,family=binomial())
fit_3 <- glm(model_3, data=tmp_df,family=binomial())

stargazer(
  fit_1, fit_2, fit_3,
  title="A Handsome Model Summary Table",
  header=FALSE,
  single.row = TRUE
)

```

`r lorem::ipsum(1, avg_words_per_sentence = 20)`

```{r, echo=FALSE, eval=TRUE}

predictions <- predict(fit_1, tmp_df, type = 'response')
conf_matrix <- table(tmp_df$trump_int, predictions> 0.5)
accuracy <- sum(diag(conf_matrix)) / sum(conf_matrix)

```

# Application


The first model as an accuracy of `r round(accuracy*100, 3)`%. Is it any good? Or is it bad? Why? `r lorem::ipsum(2, avg_words_per_sentence = 14)`

```{r, eval=TRUE, echo=FALSE, size="small", fig.cap="What's wrong with this figure?"}

plot_df <- tibble(trump_int = tmp_df$trump_int, predicted_prob = predict(fit_1, tmp_df, type="resp"))

ggplot(plot_df, aes(x=predicted_prob, y=trump_int)) +
  geom_jitter(width=0.025, height=.2, shape=1, alpha=.3) +
  geom_smooth(method="glm", method.args=list(family="binomial"), fullrange=TRUE, color="red", alpha=.8) +
  ylab("Voting Intention for Trump") +
  scale_y_continuous(breaks=c(0,1)) +
  scale_x_continuous(breaks=c(0,1)) +
  xlab("Predicted Probability") +
  theme_minimal()
```

`r lorem::ipsum(1, avg_words_per_sentence = 15)`

# Conclusion and Discussion



`r lorem::ipsum(5, avg_words_per_sentence = 16)`

<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
