---
title: "An strange article about a template with a very bad title"
author:
- name: Jane Doe
  affiliation: Some University
abstract: "This document serves as a template that you can reuse with your own projects.  The goal is to illustrate some of the functionalities of R, LaTeX, and Rmarkdown to conduct end-to-end academic research projects. You will also use this template for some of the course assignments and also to do your research project. There are many different moving pieces when you use this document for the first time. Don't worry if you don't understand everything yet."
keywords: "GitHub, LaTex, R, Rmarkdown, RStudio"
date: "`r format(Sys.time(), '%B %d, %Y')`"
bibliography: references.bib
biblio-style: apsr

geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
endnote: no
output:
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: latex-template.tex
header-includes:
  -  \usepackage{hyperref}
# spacing: double
---

```{r setup, include=FALSE}
# Compiling options
knitr::opts_chunk$set(cache=TRUE,
                      message=FALSE, warning=FALSE,
                      fig.path='figs/',
                      cache.path = '_cache/',
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })
```


# Introduction

Theories of political disagreement often envisage ideology as a single, latent dimension that structures politics on a continuum between left and right [@downs1957economic]. `r lorem::ipsum(5, avg_words_per_sentence = 20)`

## Existing work

## Research question

This is some random text.

$H_1$: Given what we know, we expect something to happen.

$H_2$: We might expect another thing to happen.

$H_3$: ...

# Data and Methods

# Results

# Conclusion and Discussion

Can we also use footnotes [^one_footnote] in Rmarkdown? Well, yes and here's another one.[^another_footnote]

[^one_footnote]: I really hope that you noticed this footnote.
[^another_footnote]: Some extra random text, just to make sure you see these little footnotes.

What about citations and references?

```{markdown}

- Find your biblatexkey in your `refernces.bib` file.
- Put an @ before it, like @downs1957economic, or whatever it is.
- @downs1957economic creates an in-text citation (e.g. Downs (1957) says...)
- [@downs1957economic] creates a parenthetical citation (Downs, 1957)

```



```{r, echo=FALSE, eval=TRUE, tidy = TRUE, size="small", cache=FALSE, results="asis", message=F, warning=F}
library(stargazer)
stargazer(lm(speed~dist, data=cars), title="A Handsome Table", header=FALSE)
```

<!--
# References
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->
